Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-07 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

% Hier vielleicht auch noch Fig. 3 aus der ACSNano-Publikation einfügen??? Würde vielleicht ganz
% gut passen!?

>>>>

% Hier kommt jetzt Fig. 3 aus der ACSNano-Publikation. @Patrick: Dafür bräuchten wir dann auch die 
% Rechte + davon hast du glaube ich auch die Original-PDF-Version!?

\begin{figure}
  \centering
%   \includegraphics[clip,scale=1]{.PDF} % @Patrick hier bitte auch den entsprechenden Filename 
% eintragen
    \caption{
    \textbf{Simulating diffraction-limited and subdiffraction recordings of a protein involved in 
    membrane protrusion formation.} 
    (\textbf{A}) Topographical image of a membrane protrusion on the surface of a HeLa cell. The 
    black traces indicate the putative location of a hypothetical protein, that could be involved 
    in the formation of the membrane protrusion. (\textbf{B}) Simulated diffraction-limited 
    recording of the hypothetical protein (resolution 250~nm). (\textbf{C}) Simulated 
    subdiffraction recording of the hypothetical protein (resolution 75~nm). The scale bar in A 
    applies to all images \newline Reprinted with permission from \emph{Philipp Hagemann*, Astrid 
    Gesper*, Patrick Happel}, Correlative stimulated emission depletion and scanning ion 
    conductance microscopy, \emph{ACS Nano} 2018, 12, 5807-5815, DOI: 10.1021/acsnano.8b01731. 
    Copyright 2020 American Chemical Society}
  \label{fig:structure_element_FM_vs_SRFM}
\end{figure}

\subsection{Combining SICM with STED microscopy}
